\MakeUppercase{Notes on Layered $H$-Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-04 k-planar.tex
(t,\ell) instead of (\ell,t)
Fixed boundary issue with where an edge appears

Let $K$ be the PS-partition for $G^+$ and $T$.  We say that a vertex $v\in V(G)$ \emph{appears} at a node $x\in V(K)$ if $u\in Y_x$ or if there exists $vw\in E(G)$ such that $v,w\in V(N_x)\setminus V(F_x)$ and $vw$ crosses $Y_x$ (i.e,. $vw$ contains a dummy vertex of $V(Y_x)$ in its interior).

Let $S_x$ (the separator at $x$) denote the set of all vertices $v\in V(G)$ such that $v$ appears at $x$ but does not appear at an ancestor of $x$.  We claim that $(S_x:x\in V(K))$ is a partition of $V(G)$.  Indeed, any $v\in V(G)$ can only appear in a node $x$ such that $v\in V(N_x)\setminus V(F_x)$.  These nodes form a path from the root of $K$ to the unique node $x'$ such that $v\in Y_{x'}$.  It is worth noting that, if $vw\in E(G)$, and $v,w\in S_x$, then the embedding of $vw$ is contained in the interior of $F_x$ (otherwise $v$ and $w$ would have appeared in $S_a$ for some ancestor $a$ of $x$.)

@@

\begin{thm}
    Every $k$-planar graph $G$ has a $(3k,k9^{2k+1}/8)$-partition.
\end{thm}

>>>>

Let $K$ be the PS-partition for $G^+$ and $T$.  We say that a vertex $v\in V(G)$ \emph{appears} at a node $x\in V(K)$ if $u\in Y_x$ or if there exists $vw\in E(G)$ such that $v,w\in V(N_x)$ and $vw$ contains a vertex of $Y_x$, either as an endpoint or in its interior.

Let $S_x$ (the separator at $x$) denote the set of all vertices $v\in V(G)$ such that $v$ appears at $x$ but does not appear at an ancestor of $x$.  We claim that $(S_x:x\in V(K))$ is a partition of $V(G)$. Indeed, if $v$ appears at nodes $x$ and $y$ where neither $x$ nor $y$ is an ancestor of the other, the $v$ contains a vertex of $Y_a$ for some common ancestor $a$ of $x$ and $y$.

@@

\begin{thm}
    Every $k$-planar graph $G$ has a $(k9^{2k+1}/8,3k)$-partition.
\end{thm}
